### 2021-05-14 README.Rmd
Add Global Policy DOI

[![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FSM5EW-blue)](https://doi.org/10.17605/OSF.IO/SM5EW) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4064840.svg)](https://doi.org/10.5281/zenodo.4064840)

> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW)

@@

>>>>

[![Global Policy DOI](https://img.shields.io/badge/Global%20Policy%20DOI-10.1111%2F1758--5899.12984-brightgreen)](https://doi.org/10.1111/1758-5899.12984) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FSM5EW-blue)](https://doi.org/10.17605/OSF.IO/SM5EW) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4064840.svg)](https://doi.org/10.5281/zenodo.4064840)

> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi:[10.1111/1758-5899.12984](https://doi.org/10.1111/1758-5899.12984)

@@

The paper is published at *Global Policy*:

> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi:[10.1111/1758-5899.12984](https://doi.org/10.1111/1758-5899.12984)
